Thesis outline

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Added acknowledgments and dedication

\chapter[O$^+$ approximation]{Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass}\label{ch:Paper3}

This chapter has been submitted to the \emph{Astrophysical Journal} by Kelly A. 
Douglass, Michael S. Vogeley, and Renyue Cen; it will be referenced as Douglass 
et. al (2017).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    THEORY
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Theory]{Estimation of gas-phase chemical abundances from optical spectroscopy}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{Images/Paper3/Zlow_v_Zreal_1sig_I06_BPTclass_fits}
    \caption[O$^++$/H versus O/H]{$12 + \log{\text{O}^{++}/\text{H}}$ versus \OH 
    for those galaxies with $M_r > -20$ as calculated with the direct method; 
    the galaxies are colored by their classification in the BPT diagrams 
    \citep[from][]{Brinchmann04}.  Two linear models have been fit to three 
    groups in the sample: star-forming and AGN/composite galaxies; the best fit 
    parameters can be found in Table \ref{tab:ab}.}
    \label{fig:lowVreal}
\end{figure}

@@

    \begin{tabular}{ccccccc}
        Environment & Average & Median & Average Shift\footnote{Wall -- Void (Positive shifts indicate that the wall values are greater than the void values; negative shifts indicate that the void values are greater than the wall values.)} & Median Shift & $p$-value & K-S Test Statistic\\
        \hline
        % Oxygen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \hline
        \multicolumn{7}{c}{\OH}\\
        \hline
        Void & $7.99\pm 0.007$ & 8.06 & \multirow{2}{*}{$-0.03\pm 0.012$} & \multirow{2}{*}{-0.03} & \multirow{2}{*}{0.1197} & \multirow{2}{*}{0.0569}\\
        Wall & $7.96\pm 0.009$ & 8.04 & & & & \\
        % Nitrogen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \hline
        \multicolumn{7}{c}{\NH}\\
        \hline
        Void & $6.55\pm 0.007$ & 6.58 & \multirow{2}{*}{$0.04\pm 0.011$} & \multirow{2}{*}{0.02} & \multirow{2}{*}{0.0149} & \multirow{2}{*}{0.0750}\\
        Wall & $6.58\pm 0.008$ & 6.60 & & & & \\
        % N/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \hline
        \multicolumn{7}{c}{\NO}\\
        \hline
        Void & $-1.45\pm 0.010$ & -1.43 & \multirow{2}{*}{$0.07\pm 0.016$} & \multirow{2}{*}{0.06} & \multirow{2}{*}{0.0003} & \multirow{2}{*}{0.1013}\\
        Wall & $-1.38\pm 0.012$ & -1.37 & & & & \\
    \end{tabular}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{Images/Paper3/1sig_dwarf_I06relations_SF_t3_T04comparison_dust}
    \caption[Comparison of O$^+$ approximation metallicities to 
    \cite{Tremonti04}]{Oxygen abundance comparison between our calculated 
    estimates with the O$^+$ approximation and those made by \cite{Tremonti04}.  
    Error bars have been omitted for clarity.  While the majority of our 
    abundance estimates agree reasonably well with the values already published, 
    it is clear that our estimates are often lower than the previously published 
    values.  It is well known that the strong-line methods \citep[like those 
    used by][]{Tremonti04} overestimate the oxygen abundance by as much as 0.3 
    dex \citep{Kennicutt03}.  Therefore, it is not surprising that the oxygen 
    abundances measured using the direct $T_e$ method are lower, particularly at 
    very low metallicities.}
    \label{fig:T04_comp}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{Images/Paper3/1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_logNO_scatterMbin}
    \caption[O/H versus N/O for star-forming dwarf galaxies]{Oxygen abundance 
    (\OH) versus the N/O ratio (\NO) for the dwarf galaxies in this study; the 
    average values of the galaxies' abundances when binned by stellar mass in 
    bins of width 0.1 are also shown.  As seen in \cite{Andrews13} and 
    \cite{Douglass17b}, while most of the mass bins are scattered together 
    around \NO $\sim$-1.5, there is a negative correlation between these two 
    abundance ratios.  There is no evidence of secondary nitrogen production in 
    this sample of star-forming dwarf galaxies, which would manifest as a 
    positive relationship between O/H and N/O at high metallicities.}
    \label{fig:NOvOH}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/Paper3/1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_N12logNH_scatterMbin}
    \caption[O/H versus N/H for star-forming dwarf galaxies]{Oxygen abundance 
    (\OH) versus nitrogen abundance (\NH) for the dwarf galaxies in this study; 
    the average values of the galaxies' abundances when binned by their stellar 
    mass in bins of width 0.1 are also shown.  There is evidence of two 
    evolutionary tracks for the star-forming dwarf galaxies here, one with a 
    much steeper slope than the other.}
    \label{fig:OvN_P3}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    DISCUSSION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Discussion]{Large-scale environmental influence}

>>>>

\chapter[O$^+$ Approximation]{Large-Scale Environmental Dependence of Chemical Abundances in Dwarf Galaxies and Implications for Connecting Star Formation and Halo Mass}\label{ch:Paper3}

This chapter has been submitted to the \emph{Astrophysical Journal} by Kelly A. 
Douglass, Michael S. Vogeley, and Renyue Cen; it will be referenced as Douglass 
et. al (2017, submitted).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    THEORY
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Abundance calculations]{Estimation of gas-phase chemical abundances from optical spectroscopy}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper3/Zlow_v_Zreal_1sig_I06_BPTclass_fits}
    \caption[O$^++$/H versus O/H]{$12 + \log{\text{O}^{++}/\text{H}}$ versus \OH 
    for those galaxies with $M_r > -20$ as calculated with the direct method; 
    the galaxies are colored by their classification in the BPT diagrams 
    \citep[from][]{Brinchmann04}.  Two linear models have been fit to three 
    groups in the sample: star-forming and AGN/composite galaxies; the best fit 
    parameters can be found in Table \ref{tab:ab}.}
    \label{fig:lowVreal}
\end{figure}

@@

    \begin{tabular}{ccccccc}
        Environment & Average & Median & Average Shift\footnote{Wall -- Void (Positive shifts indicate that the wall values are greater than the void values; negative shifts indicate that the void values are greater than the wall values.)\label{fnote_P3}} & Median Shift\textsuperscript{\ref{fnote_P3}} & $p$-value & K-S Test Statistic\\
        \hline
        % Oxygen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \hline
        \multicolumn{7}{c}{\OH}\\
        \hline
        Void & $7.99\pm 0.007$ & 8.06 & \multirow{2}{*}{$-0.03\pm 0.012$} & \multirow{2}{*}{-0.03} & \multirow{2}{*}{0.1197} & \multirow{2}{*}{0.0569}\\
        Wall & $7.96\pm 0.009$ & 8.04 & & & & \\
        % Nitrogen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \hline
        \multicolumn{7}{c}{\NH}\\
        \hline
        Void & $6.55\pm 0.007$ & 6.58 & \multirow{2}{*}{$0.04\pm 0.011$} & \multirow{2}{*}{0.02} & \multirow{2}{*}{0.0149} & \multirow{2}{*}{0.0750}\\
        Wall & $6.58\pm 0.008$ & 6.60 & & & & \\
        % N/O %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \hline
        \multicolumn{7}{c}{\NO}\\
        \hline
        Void & $-1.45\pm 0.010$ & -1.43 & \multirow{2}{*}{$0.07\pm 0.016$} & \multirow{2}{*}{0.06} & \multirow{2}{*}{0.0003} & \multirow{2}{*}{0.1013}\\
        Wall & $-1.38\pm 0.012$ & -1.37 & & & & \\
    \end{tabular}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper3/1sig_dwarf_I06relations_SF_t3_T04comparison_dust}
    \caption[Comparison of O$^+$ approximation metallicities to 
    \cite{Tremonti04}]{Oxygen abundance comparison between our calculated 
    estimates with the O$^+$ approximation and those made by \cite{Tremonti04}.  
    Error bars have been omitted for clarity.  While the majority of our 
    abundance estimates agree reasonably well with the values already published, 
    it is clear that our estimates are often lower than the previously published 
    values.  It is well known that the strong-line methods \citep[like those 
    used by][]{Tremonti04} overestimate the oxygen abundance by as much as 0.3 
    dex \citep{Kennicutt03}.  Therefore, it is not surprising that the oxygen 
    abundances measured using the direct $T_e$ method are lower, particularly at 
    very low metallicities.}
    \label{fig:T04_comp}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper3/1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_logNO_scatterMbin}
    \caption[O/H versus N/O for star-forming dwarf galaxies]{Oxygen abundance 
    (\OH) versus the N/O ratio (\NO) for the dwarf galaxies in this study; the 
    average values of the galaxies' abundances when binned by stellar mass in 
    bins of width 0.1 are also shown.  As seen in \cite{Andrews13} and 
    \cite{Douglass17b}, while most of the mass bins are scattered together 
    around \NO $\sim$-1.5, there is a negative correlation between these two 
    abundance ratios.  There is no evidence of secondary nitrogen production in 
    this sample of star-forming dwarf galaxies, which would manifest as a 
    positive relationship between O/H and N/O at high metallicities.}
    \label{fig:NOvOH}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/Paper3/1sig_I06relations_dwarf_SF_t3_dust_NSA_Z12logOH_N12logNH_scatterMbin}
    \caption[O/H versus N/H for star-forming dwarf galaxies]{Oxygen abundance 
    (\OH) versus nitrogen abundance (\NH) for the dwarf galaxies in this study; 
    the average values of the galaxies' abundances when binned by their stellar 
    mass in bins of width 0.1 are also shown.  There is evidence of two 
    evolutionary tracks for the star-forming dwarf galaxies here, one with a 
    much steeper slope than the other.}
    \label{fig:OvN_P3}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    DISCUSSION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Environmental influence]{Large-scale environmental influence}

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Added acknowledgments and dedication

\chapter[Small-scale environment]{The influence of the small-scale environment on dwarf galaxy evolution}\label{ch:smallScaleEnvironment}

@@

\section[Introduction]{Introduction}

@@

\section[Data]{SDSS Data and galaxy selection}

% SDSS
%The Sloan Digital Sky Survey Data Release 7 \citep[SDSS DR7;][]{Abazajian09} is 
%a wide-field multiband imaging and spectroscopic survey which maps approximately 
%one-quarter of the northern sky using a drift scanning technique.  Photometric 
%data in the five-band SDSS system --- $u$, $g$, $r$, $i$, and $z$ --- is taken 
%on a dedicated 2.5m telescope at the Apache Point Observatory in New Mexico 
%\citep{Fukugita96,Gunn98}.  Galaxies with Petrosian $r$-band magnitudes 
%$m_r < 17.77$ are selected for follow-up spectroscopic analysis \citep{Lupton01,
%Strauss02}.  The galaxy colors are taken from the Korean Institute for Advanced 
%Study Value-Added Galaxy Catalog \citep[KIAS-VAGC;][]{Choi10}, which contains 
%galaxies from the SDSS DR7 main sky survey based on the New York University 
%Value-Added Galaxy Catalog Data Release 7 \citep[NYU-VAGC;][]{Blanton05}.  Total 
%star formation rates (SFR) and total specific star formation rates (sSFR) are 
%from the MPA-JHU value-added catalog\footnote{Available at 
%\url{http://www.mpa-garching.mpg.de/SDSS/DR7/}}, calculated using the technique 
%described in \cite{Brinchmann04}.  
The gas-phase chemical abundances used are from Douglass, Vogeley, and Cen 
(2017, in prep.), which are calculated using the Direct $T_e$ method.  The 
galaxies' large-scale environments are based on the void catalog compiled by 
\cite{Pan12}, which is constructed from SDSS DR7 using the VoidFinder algorithm 
of \cite{Hoyle02}.  Galaxies that are located within identified voids are 
labeled as void galaxies, and those that do not fall within a void are 
designated as a wall galaxy.  The large-scale environment within 5 \hMpc of the 
edge of the main SDSS DR7 footprint cannot be described using the VoidFinder 
algorithm because the minimum diameter of a void is 10 \hMpc.  Therefore, the 
large-scale environment for galaxies within 5 \hMpc of the edge of the main 
footprint in SDSS DR7 is designated as unknown.

@@

Two galaxy samples are used in this analysis.  The largest one contains the 
11,845 dwarf galaxies spectroscopically observed in SDSS DR7.  The second sample 
contains those star-forming dwarf galaxies from the first set that have 
gas-phase chemical abundances in Douglass et al. (2017, in prep.), totaling 2506 
dwarf galaxies.  While this subset of galaxies contains only star-forming 
galaxies and is not representative of all dwarf galaxies, we show in Section 
\ref{sec:selection_effects} that this does not affect our results.

@@

\section[Results]{Distance analysis and results}

@@

Based on our hypothesis that galaxies would be bluer and have higher sSFRs at 
small distances to their nearest neighbors, we anticipated that the metallicity 
of the galaxies would decrease with increasing distance.  As before, we only see 
a relationship between the distance and metallicity in the smallest distance 
bin in Fig. \ref{fig:OH}.  The linear fits quantify this observation --- the 
slopes are on the order of 10$^{-2}$.  Within a distance of 0.05 \hMpc or 
0.1$r_{vir}$, dwarf galaxies tend to have higher metallicities than at further 
distances from their nearest neighbor.  At distances less than 0.1 \hMpc from 
the center of the nearest group, dwarf galaxies might have lower than average 
metallicities.  However, this could be an erroneous conclusion due to 
small-number statistics.  In these distance comparisons, there is a shift 
towards higher metallicities in the void dwarf galaxies when compared to the 
wall dwarf galaxies, as has been observed by \cite{Douglass17b} and Douglass et 
al. (2017, in prep).

@@

It was expected that the gas-phase nitrogen abundance would follow the same 
trend as the metallicity, to decrease with increasing distance.  As observed 
with the other parameters, Fig. \ref{fig:NH} shows very little relationship 
between the distance and N/H, except in the smallest distance bin for the 
closest virial neighbor.  The linear fits quantify this observation --- the 
slopes are on the order of 10$^{-2}$.  Within a distance of 0.1$r_{vir}$, dwarf 
galaxies tend to have higher nitrogen abundances than at distances further from 
their nearest neighbor.  There does not seem to be any relationship between the 
nitrogen abundance of the star-forming dwarf galaxies and distance to the center 
of the nearest group.  Unlike the shifts seen with the other parameters and what 
is observed in \cite{Douglass17b} and Douglass et al. (2017, in prep), we see no 
significant difference in the nitrogen abundance resulting from the large-scale 
environment.

@@

We do not expect any influence on the relative synthesis of oxygen and nitrogen 
from the proximity to a nearest neighbor since nucleosynthesis is a physical 
process unaffected by external influences.  Unlike the other parameters studied, 
Fig. \ref{fig:NO} shows that the N/O ratio does not have any relationship with 
the distance to a nearest neighbor at any separation.  This is reflected in the 
linear fits to the data --- the slopes are on the order of 10$^{-2}$ and 
smaller.  When looking at the relationship between the N/O ratio and the 
distance to the nearest group, though, the N/O ratio might be higher than 
average in galaxies within 0.1 \hMpc of the group's center.  The shift towards 
lower N/O ratios in star-forming void dwarf galaxies is readily apparent, as 
found by \cite{Douglass17b} and Douglass et al. (2017, in prep).

@@

% Spectroscopic sample v. complete sample
\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/ALLdwarf_ur_300}
    \caption[Color versus distance of full SDSS dwarf population]{Color versus 
    distance to the nearest galaxy (in units of \hMpc on top and virial radii on 
    the bottom) for the entire dwarf galaxy population in SDSS DR7.  When 
    compared to the left-hand panel of Fig. \ref{fig:ur}, we see that there is 
    no difference in the results of the analysis by studying only star-forming 
    galaxies with sufficient detection of the various emission lines necessary 
    to estimate the gas-phase chemical abundances.}
    \label{fig:ur_allDwarf}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/dwarf_ur_xyz}
    \caption[Color versus distance calculated with redshift]{Color versus 
    distance to the nearest galaxy (in units of \hMpc on top and virial radii on 
    the bottom) for the star-forming dwarf galaxies.  The redshift is included 
    when calculating the distance to the nearest neighbor.  While there is still 
    no correlation between distance and color, we do note that there is a gap in 
    the distribution of galaxies around a distance of 0.05 \hMpc or 0.1$r_{vir}$ 
    from the nearest neighbor.}
    \label{fig:ur_xyz}
\end{figure}

@@

\section[Discussion]{Discussion}

@@

\section[Conclusions]{Conclusions}

Using the star-forming dwarf galaxies in the SDSS DR7 sample with gas-phase 
chemical abundances from Douglass et al. (2017, in prep), we investigate the 
influence of the small-scale environment on the evolution of dwarf galaxies.  
From the $\sim$2000 galaxies in the sample, there only appears to be an effect 
from a neighboring galaxy within 0.05 \hMpc or 0.1$r_{vir}$.  The proximity of a 
group seems to only affect the target dwarf galaxy if it is within 0.1 \hMpc.  
Thus, the small-scale ($\sim 1$ \hMpc) environment does not appear to strongly 
influence the evolution of dwarf galaxies.

>>>>

\chapter[Small-Scale Environment]{The Influence of the Small-Scale Environment on Dwarf Galaxy Evolution}\label{ch:smallScaleEnvironment}

@@

\section{Introduction}

@@

\section[SDSS Data]{SDSS Data and galaxy selection}

% SDSS
%The Sloan Digital Sky Survey Data Release 7 \citep[SDSS DR7;][]{Abazajian09} is 
%a wide-field multiband imaging and spectroscopic survey which maps approximately 
%one-quarter of the northern sky using a drift scanning technique.  Photometric 
%data in the five-band SDSS system --- $u$, $g$, $r$, $i$, and $z$ --- is taken 
%on a dedicated 2.5m telescope at the Apache Point Observatory in New Mexico 
%\citep{Fukugita96,Gunn98}.  Galaxies with Petrosian $r$-band magnitudes 
%$m_r < 17.77$ are selected for follow-up spectroscopic analysis \citep{Lupton01,
%Strauss02}.  The galaxy colors are taken from the Korean Institute for Advanced 
%Study Value-Added Galaxy Catalog \citep[KIAS-VAGC;][]{Choi10}, which contains 
%galaxies from the SDSS DR7 main sky survey based on the New York University 
%Value-Added Galaxy Catalog Data Release 7 \citep[NYU-VAGC;][]{Blanton05}.  Total 
%star formation rates (SFR) and total specific star formation rates (sSFR) are 
%from the MPA-JHU value-added catalog\footnote{Available at 
%\url{http://www.mpa-garching.mpg.de/SDSS/DR7/}}, calculated using the technique 
%described in \cite{Brinchmann04}.  
The gas-phase chemical abundances used are from Douglass, Vogeley, and Cen 
(2017, submitted), which are calculated using the Direct $T_e$ method.  The 
galaxies' large-scale environments are based on the void catalog compiled by 
\cite{Pan12}, which is constructed from SDSS DR7 using the VoidFinder algorithm 
of \cite{Hoyle02}.  Galaxies that are located within identified voids are 
labeled as void galaxies, and those that do not fall within a void are 
designated as a wall galaxy.  The large-scale environment within 5 \hMpc of the 
edge of the main SDSS DR7 footprint cannot be described using the VoidFinder 
algorithm because the minimum diameter of a void is 10 \hMpc.  Therefore, the 
large-scale environment for galaxies within 5 \hMpc of the edge of the main 
footprint in SDSS DR7 is designated as unknown.

@@

Two galaxy samples are used in this analysis.  The largest one contains the 
11,845 dwarf galaxies spectroscopically observed in SDSS DR7.  The second sample 
contains those star-forming dwarf galaxies from the first set that have 
gas-phase chemical abundances in Douglass et al. (2017, submitted), totaling 2506 
dwarf galaxies.  While this subset of galaxies contains only star-forming 
galaxies and is not representative of all dwarf galaxies, we show in Section 
\ref{sec:selection_effects} that this does not affect our results.

@@

\section[Analysis \& Results]{Distance analysis and results}

@@

Based on our hypothesis that galaxies would be bluer and have higher sSFRs at 
small distances to their nearest neighbors, we anticipated that the metallicity 
of the galaxies would decrease with increasing distance.  As before, we only see 
a relationship between the distance and metallicity in the smallest distance 
bin in Fig. \ref{fig:OH}.  The linear fits quantify this observation --- the 
slopes are on the order of 10$^{-2}$.  Within a distance of 0.05 \hMpc or 
0.1$r_{vir}$, dwarf galaxies tend to have higher metallicities than at further 
distances from their nearest neighbor.  At distances less than 0.1 \hMpc from 
the center of the nearest group, dwarf galaxies might have lower than average 
metallicities.  However, this could be an erroneous conclusion due to 
small-number statistics.  In these distance comparisons, there is a shift 
towards higher metallicities in the void dwarf galaxies when compared to the 
wall dwarf galaxies, as has been observed by \cite{Douglass17b} and Douglass et 
al. (2017, submitted).

@@

It was expected that the gas-phase nitrogen abundance would follow the same 
trend as the metallicity, to decrease with increasing distance.  As observed 
with the other parameters, Fig. \ref{fig:NH} shows very little relationship 
between the distance and N/H, except in the smallest distance bin for the 
closest virial neighbor.  The linear fits quantify this observation --- the 
slopes are on the order of 10$^{-2}$.  Within a distance of 0.1$r_{vir}$, dwarf 
galaxies tend to have higher nitrogen abundances than at distances further from 
their nearest neighbor.  There does not seem to be any relationship between the 
nitrogen abundance of the star-forming dwarf galaxies and distance to the center 
of the nearest group.  Unlike the shifts seen with the other parameters and what 
is observed in \cite{Douglass17b} and Douglass et al. (2017, submitted), we see no 
significant difference in the nitrogen abundance resulting from the large-scale 
environment.

@@

We do not expect any influence on the relative synthesis of oxygen and nitrogen 
from the proximity to a nearest neighbor since nucleosynthesis is a physical 
process unaffected by external influences.  Unlike the other parameters studied, 
Fig. \ref{fig:NO} shows that the N/O ratio does not have any relationship with 
the distance to a nearest neighbor at any separation.  This is reflected in the 
linear fits to the data --- the slopes are on the order of 10$^{-2}$ and 
smaller.  When looking at the relationship between the N/O ratio and the 
distance to the nearest group, though, the N/O ratio might be higher than 
average in galaxies within 0.1 \hMpc of the group's center.  The shift towards 
lower N/O ratios in star-forming void dwarf galaxies is readily apparent, as 
found by \cite{Douglass17b} and Douglass et al. (2017, submitted).

@@

% Spectroscopic sample v. complete sample
\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/smallScaleEnvironment/ALLdwarf_ur_300}
    \caption[Color versus distance of full SDSS dwarf population]{Color versus 
    distance to the nearest galaxy (in units of \hMpc on top and virial radii on 
    the bottom) for the entire dwarf galaxy population in SDSS DR7.  When 
    compared to the left-hand panel of Fig. \ref{fig:ur}, we see that there is 
    no difference in the results of the analysis by studying only star-forming 
    galaxies with sufficient detection of the various emission lines necessary 
    to estimate the gas-phase chemical abundances.}
    \label{fig:ur_allDwarf}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/smallScaleEnvironment/dwarf_ur_xyz}
    \caption[Color versus distance calculated with redshift]{Color versus 
    distance to the nearest galaxy (in units of \hMpc on top and virial radii on 
    the bottom) for the star-forming dwarf galaxies.  The redshift is included 
    when calculating the distance to the nearest neighbor.  While there is still 
    no correlation between distance and color, we do note that there is a gap in 
    the distribution of galaxies around a distance of 0.05 \hMpc or 0.1$r_{vir}$ 
    from the nearest neighbor.}
    \label{fig:ur_xyz}
\end{figure}

@@

\section[Environmental influence]{Small-scale environmental influence}

@@

\section{Conclusions}

Using the star-forming dwarf galaxies in the SDSS DR7 sample with gas-phase 
chemical abundances from Douglass et al. (2017, submitted), we investigate the 
influence of the small-scale environment on the evolution of dwarf galaxies.  
From the $\sim$2000 galaxies in the sample, there only appears to be an effect 
from a neighboring galaxy within 0.05 \hMpc or 0.1$r_{vir}$.  The proximity of a 
group seems to only affect the target dwarf galaxy if it is within 0.1 \hMpc.  
Thus, the small-scale ($\sim 1$ \hMpc) environment does not appear to strongly 
influence the evolution of dwarf galaxies.
